A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-10 paper.tex
Remove listings

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} is made for the product launching and trading. The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract. Listing. \ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.

The transparency of smart contracts bring advantages for data providers and consumers. One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively. For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has. The consumer list and the states of products, which includes \textit{Launched, KeyCertified, Finished} and \textit{Refunded} are key reputation referenced for data consumers to decide whether to subscribe.

\lstdefinestyle{solidity}{
	captionpos=b,
	tabsize=4,
	basicstyle=\scriptsize
}
\lstset{style=solidity}
\begin{lstlisting}[caption={Product Contract data fields}, label={lst:constructor}, frame=single]
contract Product {
    address public broker;
    address public provider;
    bool isBrokerWithdraw;
    bool isProviderWithdraw;
    address[] consumers;

    struct Purchase {
        bool affirmativeVote;
        bool isConsumerWithdraw;
        bool isKeyAdded;
        bool isSubscribe;
        string encryptKey;
    }
    mapping(address => Purchase) public consumer2Purchase;

    uint public price;
    uint public totalAmount;
    uint public brokerage;
    uint public cancellation;
    uint public threshold;
    string public channelRoot;
    string public endPoint;
    uint public totalNumber;
    uint public uploadedNumber;
    uint public affirmativeVotes;
    string hashedKey;
    string certifiedKey;

    enum State {Launched, KeyCertified, Finished, Refunded}
    State public state;
}
\end{lstlisting}

@@

The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract. As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract. This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one. The workflow is shown in Fig.~\ref{fig:launching_product} and the certification codes in Product Contract is in Listing.~\ref{lst:key_certification}. Finally, the data product is launched and data providers can start uploading data.

>>>>

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} is made for the product launching and trading. The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract. Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.

The transparency of smart contracts bring advantages for data providers and consumers. One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively. For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has. The consumer list and the states of products are key reputation referenced for data consumers to decide whether to subscribe.

@@

The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract. As regard to the encryption key of data product, data providers send the hash digest of encryption key to a broker, who will then sign it and write it on the Product Contract. This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest toward data consumers with a wrong one. The workflow is shown in Fig.~\ref{fig:launching_product}. Finally, the data product is launched and data providers can start uploading data.
